Market simulator

### 2020-09-16 analysis/05_market_simulator.Rmd
Cleaning up labels, configurations now an output folder

---
title: "Why Donors Donate?"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

```{r packages, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(flexdashboard)
library(plotly)
library(shiny)
library(here)
```

```{r load data}

# Beta's of everything. The only model we care about right now
public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

# Persona Data from Market Simulator Workbook
persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_configV07.xlsx"))

# Org Data from Market Simulator Workbook
org_data <- readxl::read_xlsx(here('analysis', 'output', "org_config.xlsx"))

#Levels (This is a guess):            Means:
#   1. Amnesty International          0.805
#   2. Greenpeace                     0.923
#   3. Oxfam                          0.620
#   4. Red Cross                      1.820
#   5. Environment                   -0.444
#   6. Human Rights                  -0.164
#   7. Refugee Relief                -0.582
#   8. Financially Transparent        1.080
#   9. Accountable                    1.130
#   10. Small wealthy donors         -0.376
#   11. Government Grants            -0.252
#   12. Criticized by Government       -0.663
#   13. Under Government Crackdown   -1.011

################### Org Reactive Element ####################################

beta <- as.data.frame(matrix(rep(0), nrow = 13))

beta$levels = c("Amnesty International",
                "Greenpeace", 
                "Oxfam", 
                "Red Cross",
                # Org Issue
                "Environment", 
                "Human rights",
                "Refugee relief",
                # Financial Transparency
                "Engages in transparency",
                # Financial Accountability
                "Engages in accountability",
                # Funding
                "Handful of wealthy private donors", 
                "Government grants",
                # Gov Relations
                "Criticized by government",
                "Under government crackdown")

# Org Reactive Element
df <- reactive({

  #Amnesty International
    beta$ai_value <- 0
    # beta$ai_value[beta$levels == 'Amnesty International'] <- 1
    beta$ai_value[beta$levels %in% input$org1_id] <- 1
    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
    beta$ai_value[beta$levels %in% input$ai_account] <- 1
    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1

  #Greenpeace
    beta$gp_value <- 0
    # beta$gp_value[beta$levels == 'Greenpeace'] <- 1
    beta$gp_value[beta$levels %in% input$org2_id] <- 1
    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$gp_value[beta$levels %in% input$gp_account] <- 1
    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1

  #Oxfam
    beta$ox_value <- 0
    # beta$ox_value[beta$levels == 'Oxfam'] <- 1
    beta$ox_value[beta$levels %in% input$org3_id] <- 1
    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$ox_value[beta$levels %in% input$ox_account] <- 1
    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1

  #Redcross
    beta$rc_value <- 0
    # beta$rc_value[beta$levels == 'Red Cross'] <- 1
    beta$rc_value[beta$levels %in% input$org4_id] <- 1
    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
    beta$rc_value[beta$levels %in% input$rc_account] <- 1
    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
    beta

################### Persona Reactive Element ####################################

# Persona beta levels -----

beta_persona <- as.data.frame(matrix(rep(0), nrow = 111))

beta_persona$levels = c("Intercept",
                        # Follow National News
                        "Once a Week",
                        "At least once a day",
                        # Follow International News
                        "Sometimes",
                        "Always",
                        # News Mediums
                        "TV",
                        "Print",
                        "Online (not social media)",
                        "Social media",
                        "Radio",
                        "Email newsletter",
                        "News app",
                        # Follow Government or Public Affairs
                        "Often", 
                        # Travel to developing Countries
                        "Yes (1)", 
                        # Political Preference
                        "Somewhat liberal",
                        "Slightly liberal",
                        "Moderate",
                        "Slightly conservative",
                        "Somewhat conservative",
                        "Extremely conservative",
                        # Trust in Political Institute
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust (1)",
                        # Should Others be Charitable
                        "Disagree",
                        "Somewhat disagree",
                        "Nuetral",
                        "Somewhat agree",
                        "Agree",
                        "Strongly agree",
                        # Worship Service Attendance
                        "Rarely",
                        "At least once a month (1)",
                        # Religious Importance
                        "Important",
                        # Religion
                        "Protestant",
                        "Christian Orthodox",
                        "Jewish",
                        "Muslim",
                        "Sikh",
                        "Hindu",
                        "Buddhist",
                        "Atheist",
                        "Other (Religion)",
                        # Charity Trust Importance
                        "Very unimportant",
                        "Somewhat unimportant",
                        "Nuetral",
                        "Somewhat important",
                        "Very important",
                        "Essential",
                        # Trust in Charities
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust (2)",
                        # Donation Frequency
                        "At least once a month (2)", 
                        # Donation Amount
                        "$50-$99",
                        "$100-$499",
                        "$500-$999",
                        "$1,000-$4,999",
                        "$5,000-$9,999",
                        "$10,000 +",
                        # Volunteered last 12 months
                        "Yes (2)",
                        # Volunteer Frequency
                        "Rarely",
                        "More than once a month, less than once a year",
                        "At least once a month (3)",
                        # Personal Activism
                        "Involved (1)",
                        # Family Activism
                        "Involved (2)",
                        # Religious Membership
                        "Inactive member",
                        "Active member",
                        # Sport or Recreational Membership
                        "Inactive member",
                        "Active member", 
                        # Art, Music, or Educational Membership
                        "Inactive member",
                        "Active member",
                        # Labor Union Membership
                        "Inactive member",
                        "Active member",
                        # Political Party Membership
                        "Inactive member",
                        "Active member (1)",
                        # Environmental Organization Membership
                        "Inactive member",
                        "Active member",
                        # Professional Association
                        "Inactive member",
                        "Active member",
                        # Humanitarian or Charity Membership
                        "Inactive member",
                        "Active member (2)",
                        # Consumer Organization Membership
                        "Inactive member",
                        "Active member",
                        #Other Organization Membership
                        "Inactive member",
                        "Active member",
                        # Gender
                        "Female",
                        "Transgender",
                        "Prefer not to say",
                        "Other (Gender)",
                        # Marital Status
                        "Widowed",
                        "Divorced",
                        "Separated",
                        "Never married",
                        # Education
                        "High school graduate", 
                        "Some college",
                        "2 year degree",
                        "4 year degree",
                        "Graduate or professional degree",
                        "Doctorate",
                        # Income
                        "More than median of $61,372", 
                        # Race
                        "White", 
                        "Black or African American", 
                        "American Indian or Alaska Native", 
                        "Asian", 
                        "Native Hawaiian or Pacific Islander", 
                        "Other (Race)", 
                        # Age
                        "More than median age of 36")

@@

  #Persona 1
    beta_persona$p1_value <- 0

    beta_persona$p1_value[beta_persona$levels == 'Intercept'] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1

  #Persona 2
    beta_persona$p2_value <- 0

    beta_persona$p2_value[beta_persona$levels == 'Intercept'] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_international_news] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_news_medium] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_follow_gov] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_institution_trust] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_others_charitable] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_worship_attendence] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_charity_importance] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_trust_in_charity] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_frequency] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_amount] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_12] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_frequency] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_personal_activism] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_family_activism] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religious_member] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_sport_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_art_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_labor_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_environmental_member] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_professional_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_humanitarian_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_consumer_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_other_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_gender] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_marital_status] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_education] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_income] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_race] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_age] <- 1

  #Persona 3
    beta_persona$p3_value <- 0

    beta_persona$p3_value[beta_persona$levels == 'Intercept'] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1

>>>>

---
title: "Market simulator"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

```{r load-packages, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(flexdashboard)
library(plotly)
library(shiny)
```

```{r load-data}
# Gammas of the "everything" model
public_political_social_charity_demo <- read_rds(here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

# Starting organization configuration
organization_data <- read_csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))

# Starting persona configuration
persona_data <- read_csv(here::here('analysis', 'output', 'configurations', 'persona_config01.csv'))
```

```{r organization-reactive-table}
# Placeholder for organization gammas
gamma <- as.data.frame(matrix(rep(0), nrow = 13))

# Assign level labels
gamma$levels = c(
  # Organization
  "Amnesty International",
  "Greenpeace", 
  "Oxfam", 
  "Red Cross",
  # Issue Area
  "Environment", 
  "Human rights",
  "Refugee relief",
  # Financial Transparency
  "Engages in financial transparency",
  # Financial Accountability
  "Engages in financial accountability",
  # Funding Sourcs
  "Handful of wealthy private donors", 
  "Government grants",
  # Relationship with Host Government
  "Criticized by government",
  "Under government crackdown"
)

# Organization configuration reactive element
df <- reactive({

  # Amnesty International
    gamma$ai_value <- 0
    gamma$ai_value[gamma$levels %in% input$org1_id] <- 1
    gamma$ai_value[gamma$levels %in% input$ai_issue] <- 1
    gamma$ai_value[gamma$levels %in% input$ai_fin_trans] <- 1
    gamma$ai_value[gamma$levels %in% input$ai_account] <- 1
    gamma$ai_value[gamma$levels %in% input$ai_funding] <- 1
    gamma$ai_value[gamma$levels %in% input$ai_gov_relat] <- 1

  #Greenpeace
    gamma$gp_value <- 0
    # gamma$gp_value[gamma$levels == 'Greenpeace'] <- 1
    gamma$gp_value[gamma$levels %in% input$org2_id] <- 1
    gamma$gp_value[gamma$levels %in% input$gp_issue] <- 1
    gamma$gp_value[gamma$levels %in% input$gp_fin_trans] <- 1
    gamma$gp_value[gamma$levels %in% input$gp_account] <- 1
    gamma$gp_value[gamma$levels %in% input$gp_funding] <- 1
    gamma$gp_value[gamma$levels %in% input$gp_gov_relat] <- 1

  #Oxfam
    gamma$ox_value <- 0
    # gamma$ox_value[gamma$levels == 'Oxfam'] <- 1
    gamma$ox_value[gamma$levels %in% input$org3_id] <- 1
    gamma$ox_value[gamma$levels %in% input$ox_issue] <- 1
    gamma$ox_value[gamma$levels %in% input$ox_fin_trans] <- 1
    gamma$ox_value[gamma$levels %in% input$ox_account] <- 1
    gamma$ox_value[gamma$levels %in% input$ox_funding] <- 1
    gamma$ox_value[gamma$levels %in% input$ox_gov_relat] <- 1

  #Redcross
    gamma$rc_value <- 0
    # gamma$rc_value[gamma$levels == 'Red Cross'] <- 1
    gamma$rc_value[gamma$levels %in% input$org4_id] <- 1
    gamma$rc_value[gamma$levels %in% input$rc_issue] <- 1
    gamma$rc_value[gamma$levels %in% input$rc_fin_trans] <- 1
    gamma$rc_value[gamma$levels %in% input$rc_account] <- 1
    gamma$rc_value[gamma$levels %in% input$rc_funding] <- 1
    gamma$rc_value[gamma$levels %in% input$rc_gov_relat] <- 1
    gamma

})
```

```{r persona-reactive-table}
# Placeholder for persona gammas
gamma_persona <- as.data.frame(matrix(rep(0), nrow = 111))

# Assign covariate labels
gamma_persona$levels <- c(
  "Intercept",
  # Follow national news
  "Once a week",
  "At least once a day",
  # Follow international news
  "Sometimes",
  "Always",
  # Mediums to follow news
  "TV",
  "Print",
  "Online (not social media)",
  "Social media",
  "Radio",
  "Email newsletter",
  "News app",
  # Follow government and public affairs
  "Often", 
  # Traveled to a developing country
  "Traveled to a developing country", 
  # Liberal to Conservative
  "Somewhat liberal",
  "Slightly liberal",
  "Moderate",
  "Slightly conservative",
  "Somewhat conservative",
  "Extremely conservative",
  # Trust in political institutions
  "Very little trust in political institutions",
  "Little trust in political institutions",
  "Neutral trust in political institutions",
  "Some trust in political institutions",
  "A lot of trust in political institutions",
  "Complete trust in political institutions",
  # People should be more charitable
  "Disagree",
  "Somewhat disagree",
  "Neutral",
  "Somewhat agree",
  "Agree",
  "Strongly agree",
  # Religious attendance
  "Rarely attend",
  "Attend at least once a month",
  # Importance of religion
  "Important",
  # Religion
  "Protestant",
  "Christian Orthodox",
  "Jewish",
  "Muslim",
  "Sikh",
  "Hindu",
  "Buddhist",
  "Atheist",
  "Other religion",
  # Importance of trusing charities
  "Very unimportant",
  "Somewhat unimportant",
  "Neutral",
  "Somewhat important",
  "Very important",
  "Essential",
  # Trust in charities
  "Very little trust in charities",
  "Little trust in charities",
  "Neutral trust in charities",
  "Some trust in charities",
  "A lot of trust in charities",
  "Complete trust in charities",
  # Donation frequency
  "Donate at least once a month", 
  # Donated last year
  "$50-$99",
  "$100-$499",
  "$500-$999",
  "$1,000-$4,999",
  "$5,000-$9,999",
  "$10,000 +",
  # Volunteered in past 12 months
  "Volunteered in past 12 months",
  # Volunteer frequency
  "Rarely volunteer",
  "Volunteer more than once a month, less than once a year",
  "Volunteer at least once a month",
  # History of activism
  "Personally involved",
  # History of family activism
  "Family involved",
  # Church or religious organization
  "Inactive church member",
  "Active church member",
  # Sport or recreational organization
  "Inactive sports or rec organization member",
  "Active sports or rec organization member", 
  # Art, music, or educational organization
  "Inactive art, music, or educational organization member",
  "Active art, music, or educational organization member",
  # Labor union
  "Inactive union member",
  "Active union member",
  # Political party
  "Inactive political party member",
  "Active political party member",
  # Environmental organization
  "Inactive environmental organization member",
  "Active environmental organization member",
  # Professional association
  "Inactive professional association member",
  "Active professional association member",
  # Humanitarian or charitable organization
  "Inactive humanitarian or charitable organization member",
  "Active humanitarian or charitable organization member",
  # Consumer organization
  "Inactive consumer organization member",
  "Active consumer organization member",
  # Other organization
  "Inactive member in another organization",
  "Active member in another organization",
  # Gender
  "Female",
  "Transgender",
  "Prefer not to say",
  "Other gender",
  # Marital status
  "Widowed",
  "Divorced",
  "Separated",
  "Never married",
  # Education
  "High school graduate", 
  "Some college",
  "2 year degree",
  "4 year degree",
  "Graduate or professional degree",
  "Doctorate",
  # Income
  "More than median of $61,372", 
  # Race
  "White", 
  "Black or African American", 
  "American Indian or Alaskan Native", 
  "Asian", 
  "Native Hawaiian or Pacific Islander",
  "Other race",
  # Age
  "More than median age of 36"
)

@@

  #Persona 1
    gamma_persona$p1_value <- 0

    gamma_persona$p1_value[gamma_persona$levels == 'Intercept'] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_national_news] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_international_news] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_news_medium] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_follow_gov] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_travel_developing] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_political_pref] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_institution_trust] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_others_charitable] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_worship_attendence] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religion_importance] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religion] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_charity_importance] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_trust_in_charity] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_donation_frequency] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_donation_amount] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_volunteer_12] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_volunteer_frequency] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_personal_activism] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_family_activism] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_religious_member] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_sport_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_art_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_labor_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_political_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_environmental_member] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_professional_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_humanitarian_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_consumer_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_other_member] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_gender] <- 1

    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_marital_status] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_education] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_income] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_race] <- 1
    gamma_persona$p1_value[gamma_persona$levels %in% input$p1_age] <- 1

  #Persona 2
    gamma_persona$p2_value <- 0

    gamma_persona$p2_value[gamma_persona$levels == 'Intercept'] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_national_news] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_international_news] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_news_medium] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_follow_gov] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_travel_developing] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_political_pref] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_institution_trust] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_others_charitable] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_worship_attendence] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religion_importance] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religion] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_charity_importance] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_trust_in_charity] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_donation_frequency] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_donation_amount] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_volunteer_12] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_volunteer_frequency] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_personal_activism] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_family_activism] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_religious_member] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_sport_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_art_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_labor_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_political_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_environmental_member] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_professional_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_humanitarian_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_consumer_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_other_member] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_gender] <- 1

    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_marital_status] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_education] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_income] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_race] <- 1
    gamma_persona$p2_value[gamma_persona$levels %in% input$p2_age] <- 1

  #Persona 3
    gamma_persona$p3_value <- 0

    gamma_persona$p3_value[gamma_persona$levels == 'Intercept'] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_national_news] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_international_news] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_news_medium] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_follow_gov] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_travel_developing] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_political_pref] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_institution_trust] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_others_charitable] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_worship_attendence] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religion_importance] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religion] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_charity_importance] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_trust_in_charity] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_donation_frequency] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_donation_amount] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_volunteer_12] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_volunteer_frequency] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_personal_activism] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_family_activism] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_religious_member] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_sport_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_art_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_labor_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_political_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_environmental_member] <- 1

    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_professional_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_humanitarian_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_consumer_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_other_member] <- 1
    gamma_persona$p3_value[gamma_persona$levels %in% input$p3_gender] <- 1
